A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model

### 2024-11-03 paper/paper.qmd
title update

---
title: "A Polls-of-Polls Forecast for the 2024 United States Presidential Election:Analysis of Support for Harris Factoring Pollster Differences"
author: 
  - Jiwon Choi
  - Kevin Roe
thanks: "Code and data are available at: [https://github.com/jwonc4602/2024_US_Election_Forecast](https://github.com/jwonc4602/2024_US_Election_Forecast)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---

>>>>

---
title: "A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model"
subtitle: "The Impact of Pollster Differences, Population Type, and Poll Regency on Predicting Support for Kamala Harris"
author: 
  - Jiwon Choi
  - Kevin Roe
thanks: "Code and data are available at: [https://github.com/jwonc4602/2024_US_Election_Forecast](https://github.com/jwonc4602/2024_US_Election_Forecast)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
toc: true
bibliography: references.bib
---
